### 2019-08-22 chapters/3-background.tex
Final refinements

It must be noted that functions and arrays are not built-in types. A Function is considered to be `member of the Object type that is an instance of the standard built-in Function constructor and that may be invoked as a subroutine' \citep{ecma-script}. The \mintinline{text}{Function} object is a built-in object with a \mintinline{text}{[[Call]]} internal property, which means that it can be invoked. Similarly, arrays are instances of the built-in \mintinline{text}{Array} object. Both concepts are shown in \coderef{code:background-functions-and-arrays}.

@@

\subsubsection{ToString}
JavaScript performs this conversion in a very intuitive way, as explained in \coderef{code:background-to-string-operation}. Every primitive gets converted as expected. Objects are converted into strings by calling \mintinline{text}{ToPrimtive()} with \mintinline{text}{hint = string}, as presented in \coderef{code:background-to-string-implementation}.

\begin{code}
	\jscode{code/background/javascript/type-coercion/to-string.js}
	\captionsetup{aboveskip=0pt, belowskip=10pt}
	\caption[ToString implementation]{\textbf{ToString implementation}}
	\label{code:background-to-string-implementation}
\end{code}

\begin{code}
	\jscode{code/background/javascript/type-coercion/string-conversion.js}
	\captionsetup{aboveskip=0pt, belowskip=10pt}
	\caption[ToString operation examples]{\textbf{ToString operation examples}}
	\label{code:background-to-string-operation}
\end{code}

\subsubsection{ToNumber}
\coderef{code:background-to-number-operation} presents this type of conversion. Strings and boolean values get converted in the expected way. Curiously, \mintinline{text}{undefined} will be converted into \mintinline{text}{NaN} and \mintinline{text}{null} into \mintinline{text}{0}. Similarly, objects are converted into numbers by calling \mintinline{text}{ToPrimtive()} with \mintinline{text}{hint = number}, as presented in \coderef{code:background-to-number-implementation}.

@@

\subsubsection{Object to String}
The object is first converted into a primitive value calling the \mintinline{text}{ToPrimitive()} method, using \mintinline{text}{string} as \mintinline{text}{preferredType}. The obtained primitive value is then normally converted into a \mintinline{text}{string}, as explained before in \coderef{code:background-to-string-implementation}.

\coderef{code:background-object-into-string} shows a straightforward example. On the other hand, \coderef{code:background-object-into-string-not-string-return-value} provides an example where \mintinline{text}{ToPrimitive(val, String)} does not return a \mintinline{text}{string}, either because simply \mintinline{text}{toString()} does not return a \mintinline{text}{string} or because \mintinline{text}{valueOf()} gets being called instead of \mintinline{text}{toString()}.

@@

\begin{code}
	\jscode{code/background/javascript/type-coercion/plus-operator-object.js}
	\captionsetup{aboveskip=0pt, belowskip=10pt}
	\caption[JavaScript + operator with object]{\textbf{JavaScript \mintinline{text}{+} operator with object}}
	\label{code:background-plus-operator-object-example}
\end{code}

@@

Dependencies can be installed either globally or as local dependencies of specific a JavaScript projects. NPM installs the dependencies described in the \mintinline{text}{package.json} file and local dependencies are saved in the \mintinline{text}{node_modules} directory in the project's root directory. An example of NPM's usage is shown in \coderef{code:background-npm-usage-example}. The registry contains currently more than 1 million modules and it has 11000 million downloads per week.

@@

f(1, 2);

$ npm i -g typescript
$ mv index.js index.ts
$ tsc index.ts
$ cat index.js
function f(a, b) {
    return a + b;
}
f(1, 2);

$ cat index-with-type-annotations.ts
function f(a: number, b: number) : number {
	return a + b;
}

f(1, 2);

$ tsc index-with-type-annotations.ts
$ cat index-with-type-annotations.js
function f(a, b) {
    return a + b;
}
f(1, 2);
	  \end{bashinline}
	\caption[TypeScript compilation example]{\textbf{TypeScript compilation example} - A plain JavaScript file is renamed into a TypeScript file. The TypeScript compiler will compile it into plain JavaScript again. Secondly, a \mintinline{text}{.ts} file with typed annotations gets compiled into a common JavaScript file with no annotations.}
	\label{code:background-typescript-and-javascript}
  \end{code}

>>>>

It must be noted that functions and arrays are not built-in types. A Function is considered to be `member of the Object type that is an instance of the standard built-in \mintinline{text}{Function} constructor and that may be invoked as a subroutine' \citep{ecma-script}. The \mintinline{text}{Function} object is a built-in object with a \mintinline{text}{[[Call]]} internal property, which means that it can be invoked. Similarly, arrays are instances of the built-in \mintinline{text}{Array} object. Both concepts are shown in \coderef{code:background-functions-and-arrays}.

@@

\subsubsection{ToString}
JavaScript performs this conversion in a very intuitive way, as explained in \coderef{code:background-to-string-operation}. Every primitive gets converted as expected. Objects are converted into strings by calling \mintinline{text}{ToPrimitive()} with \mintinline{text}{hint = string}, as presented in \coderef{code:background-to-string-implementation}.

\begin{code}
	\jscode{code/background/javascript/type-coercion/to-string.js}
	\captionsetup{aboveskip=0pt, belowskip=10pt}
	\caption[ToString implementation]{\textbf{ToString implementation} - If the input argument has type \mintinline{text}{object}, it will call \mintinline{text}{ToPrimitive()} with \mintinline{text}{hint = string} and then recursively call itself again.}
	\label{code:background-to-string-implementation}
\end{code}

\begin{code}
	\jscode{code/background/javascript/type-coercion/string-conversion.js}
	\captionsetup{aboveskip=0pt, belowskip=10pt}
	\caption[ToString operation examples]{\textbf{ToString operation examples} - Numbers are converted into string in an expected way. The values \mintinline{text}{true, false, null, undefined, NaN}, however, are converted into a \mintinline{text}{string} containing the value's name. This is one of the main reasons why it is common to see the words 'undefined', 'null' or 'NaN' in web applications.}
	\label{code:background-to-string-operation}
\end{code}

\subsubsection{ToNumber}
\coderef{code:background-to-number-operation} presents this type of conversion. Strings and boolean values get converted in the expected way. Curiously, \mintinline{text}{undefined} will be converted into \mintinline{text}{NaN} and \mintinline{text}{null} into \mintinline{text}{0}. Similarly, objects are converted into numbers by calling \mintinline{text}{ToPrimitive()} with \mintinline{text}{hint = number}, as presented in \coderef{code:background-to-number-implementation}.

@@

\subsubsection{Object to String}
The object is first converted into a primitive value calling the \mintinline{text}{ToPrimitive()} method, using \mintinline{text}{string} as \mintinline{text}{preferredType}. The obtained primitive value is then normally converted into a \mintinline{text}{string}, as explained before in \coderef{code:background-to-string-implementation}. \coderef{code:background-object-into-string} shows a straightforward example.

On the other hand, \coderef{code:background-object-into-string-not-string-return-value} provides an example where \mintinline{text}{ToPrimitive(val, String)} does not return a \mintinline{text}{string}, either because simply \mintinline{text}{toString()} does not return a \mintinline{text}{string} or because \mintinline{text}{valueOf()} gets being called instead of \mintinline{text}{toString()}.

@@

\begin{code}
	\jscode{code/background/javascript/type-coercion/plus-operator-object.js}
	\captionsetup{aboveskip=0pt, belowskip=10pt}
	\caption[JavaScript + operator with an object]{\textbf{JavaScript \mintinline{text}{+} operator with an object}}
	\label{code:background-plus-operator-object-example}
\end{code}

@@

Dependencies can be installed either globally or as local dependencies of specific JavaScript projects. NPM installs the dependencies described in the \mintinline{text}{package.json} file and local dependencies are saved in the \mintinline{text}{node_modules} directory in the project's root directory. An example of NPM's usage is shown in \coderef{code:background-npm-usage-example}. The registry contains currently more than 1 million modules and it has 11000 million downloads per week.

@@

f(1, 2);
$ npm i -g typescript
$ mv index.js index.ts
$ tsc index.ts
$ cat index.js
function f(a, b) {
    return a + b;
}
f(1, 2);
$ cat index-with-type-annotations.ts
function f(a: number, b: number) : number {
	return a + b;
}

f(1, 2);
$ tsc index-with-type-annotations.ts
$ cat index-with-type-annotations.js
function f(a, b) {
    return a + b;
}
f(1, 2);
	  \end{bashinline}
	\caption[TypeScript compilation example]{\textbf{TypeScript compilation example} - A plain JavaScript file is renamed into a TypeScript file. The TypeScript compiler will compile it into plain JavaScript again. Secondly, a \mintinline{text}{.ts} file with typed annotations gets compiled into a common JavaScript file with no annotations.}
	\label{code:background-typescript-and-javascript}
  \end{code}

### 2019-08-22 chapters/4-approach.tex
Final refinements

Code examples that execute the JavaScript Library are needed to extract the run-time information via code instrumentation. It is achieved by retrieving the examples provided in the README files of the repositories of the different libraries. This is generally the place where developers explicitly show how to use their code. It showed to be an appropriate and pragmatic way of extracting the developer's intention and providing an useful initial code base with meaningful examples, thus avoiding a possible cold start problem.

@@

\begin{code}
  \jscode{code/run-time-information-gathering/analysis/get-field-changing-at-runtime.js}
  \caption[Modified accessed property]{\textbf{Modified accessed property} - Variable \mintinline{text}{b} gets declared within the scope of function \mintinline{text}{foo}. Therefore, no observation on it gets stored.}
  \label{code:get-field-changing-at-runtime}
\end{code}

@@

The behavior of the original code is being explicitly modified. Therefore, original values are used instead for affected operators like \mintinline{text}{===, !==, typeof}, for which wrapper objects will not work as expected. For \mintinline{text}{null} and \mintinline{text}{undefined} wrappers, the original values are used for conditional operators, since the result of the abstract operation \mintinline{text}{ToBoolean} on an object is always \mintinline{text}{true}, as defined in the ECMAScript Language Specification \citep{ecma-script}. This approach could have been used for every operation by using the original value in the affected Jalangi callbacks. However, the implementation is complex and error prone. Instead, it was decided to modify the corresponding methods or specific operators so that they are compliant with JavaScript Type Coercion, which is explained in detail in {sec:background-js-type-coercion}.

@@

\begin{code}
\begin{bashinline}
$ ./build/build.sh
$ docker run --name generate-declaration-file \
  -v PATH_TO_RUN_TIME_INFORMATION_JSON:/tmp/output.json \
  tsd-generator \
  --module-name calculator \
  -i /tmp/output.json

$ docker cp generate-declaration-file:/usr/local/app/output/. /tmp/ts-declaration-file
$ docker rm generate-declaration-file
$ cat /tmp/ts-declaration-file/calculator/index.d.ts
export function sum(a: number, b: number): number;
export function multiply(a: number, b: number): number;
\end{bashinline}
  \caption[Declaration file generation]{\textbf{Declaration file generation} - The Docker image needs to be built after cloning the repository. Afterwards, the declaration file is generated by the run-time information and then retrieved from the container.}
  \label{code:declaration-file-generation-docker}
\end{code}

@@

\subsection{Parsing} \label{sec:approach-parsing}
Before comparison, declaration files need to be parsed so that both of them share the same structure. It was achieved by using the TypeScript Compiler API, a library developed by Microsoft that allows to traverse the Abstract Syntax Tree in an easy and intuitive way \citep{ts-compiler-api}.

>>>>

Code examples that execute the JavaScript Library are needed in order to extract the run-time information via code instrumentation. It is achieved by retrieving the examples provided in the README files of the repositories of the different libraries. This is generally the place where developers explicitly show how to use their code. It showed to be an appropriate and pragmatic way of extracting the developer's intention and providing an useful initial code base with meaningful examples, thus avoiding a possible cold start problem.

@@

\begin{code}
  \jscode{code/run-time-information-gathering/analysis/get-field-changing-at-runtime.js}
  \caption[Modified accessed property]{\textbf{Modified accessed property} - Property \mintinline{text}{bar} gets accessed twice. Two interactions are saved.}
  \label{code:get-field-changing-at-runtime}
\end{code}

@@

The behavior of the original code is being explicitly modified. Therefore, original values are used instead for affected operators like \mintinline{text}{===, !==, typeof}, for which wrapper objects will not work as expected. For \mintinline{text}{null} and \mintinline{text}{undefined} wrappers, the original values are used for conditional operators, since the result of the abstract operation \mintinline{text}{ToBoolean} on an object is always \mintinline{text}{true}, as defined in the ECMAScript Language Specification \citep{ecma-script}. This approach could have been used for every operation by using the original value in the affected Jalangi callbacks. However, the implementation is complex and error prone. Instead, it was decided to modify the corresponding methods or specific operators so that they are compliant with JavaScript Type Coercion, which is explained in detail in \secref{sec:background-js-type-coercion}.

@@

\begin{code}
\begin{bashinline}
$ ./build/build.sh
$ docker run --name generate-declaration-file \
  -v PATH_TO_RUN_TIME_INFORMATION_JSON:/tmp/output.json \
  tsd-generator --module-name calculator -i /tmp/output.json
$ docker cp generate-declaration-file:/usr/local/app/output/. /tmp/ts-declaration-file
$ docker rm generate-declaration-file
$ cat /tmp/ts-declaration-file/calculator/index.d.ts
export function sum(a: number, b: number): number;
export function multiply(a: number, b: number): number;
\end{bashinline}
  \caption[Declaration file generation]{\textbf{Declaration file generation} - The Docker image needs to be built after cloning the repository. Afterwards, the declaration file is generated by the run-time information and then retrieved from the container.}
  \label{code:declaration-file-generation-docker}
\end{code}

@@

\subsection{Parsing} \label{sec:approach-parsing}
Before comparison, declaration files need to be parsed so that both of them share the same structure. It was achieved by using the TypeScript Compiler API, a library developed by Microsoft that allows to traverse the Abstract Syntax Tree in an easy and intuitive way \citep{typescript-compiler-api}.
